Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-04-12 TEBenchmarkPaper/article.tex
Improve justification

This has applications wherever we find use for formal statements: in proof
assistants and their libraries, in mathematics education and research, and in
the specification, verification, optimisation and testing of software. Similar
tasks are also studied in Computational \emph{Scientific}
Discovery~\cite{king2004functional,Williams20141289,schmidt2009distilling},
although that relies on inductive reasoning and experimental testing which (in
principle) are not so important for pure mathematics. Whilst we \emph{have}
found these methods to also be important for MTE tools (in particular for the
\emph{plausibility} of generated conjectures), we leave a more thorough
application of our results to scientific reasoning for future work.

>>>>

This has applications wherever we find uses for formal methods: in proof
assistants and their libraries, in mathematics education and research, and in
the specification and verification of software. Although formal methods, and
automated reasoning more generally, have been advocated in mathematics (notably
by Voevodsky~\cite{voevodsky2010univalent} and
Gowers~\cite{ganesalingam2013fully}) and software engineering (for example via
dependently-typed
programming~\cite{McKinna:2006, chlipala2011certified, Xi2003}), they have a
reputation for being difficult and expensive, which has historically limited
their use to high-assurance domains such as aerospace and microprocessor design.
Increased automation is one way to address these problems, and conjecture
generation has already been shown to aid in specification and verification of
software properties~\cite{Claessen.Johansson.Rosen.ea:2013}).

Similar tasks are also studied in the domain of Computational \emph{Scientific}
Discovery~\cite{king2004functional,Williams20141289,schmidt2009distilling},
although that relies on inductive reasoning and experimental testing which (in
principle) are not so important for pure mathematics. Whilst we \emph{have}
found these methods to also be important for MTE tools (in particular for the
\emph{plausibility} of generated conjectures), we leave a more thorough
application of our results to scientific reasoning for future work.
